Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-18 manuscript_rmarkdown/manuscript.Rmd
Moved rmarkdown to its own folder.

manuscript_dir <- file.path("C:/Users/alexz/Documents/GitHub/power.transform/manuscript")
source(file.path(manuscript_dir, "simulations.R"))
source(file.path(manuscript_dir, "plots.R"))

>>>>

manuscript_dir <- file.path("C:/Users/alexz/Documents/GitHub/power.transform/manuscript_rmarkdown")
source(file.path(manuscript_dir, "simulations.R"))
source(file.path(manuscript_dir, "plots.R"))
